%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.


\documentclass[12pt,letterpaper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% modern themes
\moderncvstyle{banking}                            % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                                % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

% character encoding
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{newunicodechar}
\newunicodechar{￥}{\textyen}
\DeclareTextCommandDefault{\textyen}{%
  \vphantom{Y}%
  {\ooalign{Y\cr\hidewidth\yenbars\hidewidth\cr}}%
}

\newcommand{\yenbars}{%
  \vbox{
     \hrule height.1ex width.4em
     \kern.15ex
     \hrule height.1ex width.4em
     \kern.3ex
  }%
}

% adjust the page margins
\usepackage[scale=0.9]{geometry}
\usepackage{multicol}
\usepackage{import}
\usepackage[sort&compress,numbers]{natbib}

% personal data
\name{Esther}{XU FEI}

%\addbibresource{publications}
\newcommand*{\customcventry}[7][.25em]{
  \begin{tabular}{@{}l} 
    {\bfseries #4} {| #5}
  \end{tabular}
\\
  \begin{tabular}{@{}l} 
    { #3}
  \end{tabular}
  % Orginial right part settings
  \hfill% move it to the right
  \begin{tabular}{l@{}}
     { #2}
  \end{tabular}
  \ifx&#7&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#7%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

\newcommand*{\customcvproject}[4][.25em]{
%   \vfill\noindent
  \begin{tabular}{@{}l} 
    {\bfseries #2} { #3}
  \end{tabular}   

  \ifx&#4&%
  \else{\\%
    \begin{minipage}{\maincolumnwidth}%
      \small#4%
    \end{minipage}}\fi%
  \par\addvspace{#1}}

  
 \newcommand*{\award}[3][.25em]{
%   \vfill\noindent

    { #2} {| #3}

  % move it to the right

    

  \par\addvspace{#1}}

\setlength{\tabcolsep}{12pt}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------

% Add last updated date to header
\fancypagestyle{plain}{%
  \fancyhf{}
  \fancyhead[R]{\small\textcolor{gray}{Last updated: \today}}
  \renewcommand{\headrulewidth}{0pt}
}
\pagestyle{plain}

\makecvtitle
\vspace*{-18mm}



\begin{center}
\begin{tabular}{ c c c c }
 \faEnvelopeO\enspace estherxufei@gmail.com &  \faMobile\enspace 443-714-9400 &  \faLinkedinSquare\enspace  \href{https://www.linkedin.com/in/estherxufei/}{estherxufei} & \faGithub\enspace \href{https://github.com/Estherrrrrxu}{Estherrrrrxu} \\
\end{tabular}
\end{center}


\section{Skills}

\begin{tabular}{p{0.12\linewidth}  p{0.8\linewidth}}
\textbf{Programming:} & Python, SQL, R, MatLab, version control (Git), SLURM, \LaTeX, shell script (bash)\\
\textbf{Statistical:} & Time series analysis (ARIMA, ICA), dimension reduction (PCA), manifold learning (Isomap, diffusion map, UMAP, t-SNE), stochastic processes (MCMC, Gaussian Process), state space models (particle filters, particle MCMC)\\
\textbf{Software:} &ParFlow, Gdal/ArcGIS/QGIS, Google Earth \\
\textbf{Language:}& Chinese (native), English (fluent), and Spanish (intermediate)
\end{tabular}


\section{Education}
\customcvproject{Ph.D. in Physical Hydrology}{| Johns Hopkins University (JHU) | Aug. 2024}{}
Baltimore, MD | GPA: 3.92 / 4.00
\begin{itemize}
  \item  \textbf{M.Eng.} in Environmental Management and Economics, Department of Environmental Health and Engineering
  \item \textbf{M.Eng.} in Statistics and Statistical Learning, Department of Applied Mathematics and Statistics
\end{itemize}

\customcvproject{M.S. in Hydrology}{| New Mexico Tech (NMT) | Aug. 2018}{}
Socorro, NM | GPA: 3.93 / 4.00
\begin{itemize}
  \item \textbf{Thesis} Estimation of Focused Recharge for New Mexico Using a Soil-Water-Balance Model: PyRANA
  \item Minor in Operational Research and Statistics
\end{itemize}

\customcvproject{B.Eng. in (Petroleum) Resources Exploration Engineering}{| Yangtze University | Aug. 2017}{}
Wuhan, Hubei, China | Dual degree program with NMT

\customcvproject{B.S. in Earth Sciences with Geology option}{| NMT | Aug. 2016}{}
Socorro, NM | GPA: 3.91 / 4.00
\begin{itemize}
  \item Minor in Mathematics
\end{itemize}

\section{Working Experiences}
\customcvproject{Applied Scientist III, Amazon.com, Inc.}{}{}
Seattle, WA | Feb. 2024 – Present
\begin{itemize}
\item Leverage machine learning techniques to mitigate estimation biases in causal inference processes.
\item Conduct impact assessments on millions of Amazon customers exposed to package marketing messages through semi-randomized experiments.
\end{itemize}

\customcvproject{Applied Scientist Intern, Amazon.com, Inc.}{}{}
Seattle, WA | May 2023 – Aug. 2023
\begin{itemize}
\item Identified 5 distinct personas from a high-dimensional dataset of over 400k customers and 2k features using PySpark.
\item Integrated continuous business metrics into an automated and interpretable personalization framework, overseeing the coordination of various functional components, including dimensionality reduction (UFS), high-dimensional data transformation, and latent archetype space construction (WoE, VAE), clustering (IHC-KNN).
\item Developed a prompt in-context learning system to enhance the interpretability of the personalization pipeline.
\item Leveraged AWS SageMaker and EC2 to deploy large language models, including Falcon-40B and Llama-2-7B.
\item Collaborated with a diverse team of Product Managers, scientists, Software Development Engineers, and Data Engineers from various geographical regions.
\item Currently preparing publication for submission.
\end{itemize}

\customcvproject{Research Assistant, Johns Hopkins University (JHU)}{}{}
Baltimore, MD | Aug. 2018 – Present
\begin{itemize}
\item Conduct research in the area of Hydrology and Applied Mathematics focusing on modeling hydrological time series and time series classification through literature research, developing models, analyzing data, and academic research communication
\item Investigate flow path and nutrient cycling in natural watersheds by using mathematical methods to model complicated time series
\item Develop skills in Python programming, time series modeling, isotope analyzer operation, and field experiments
\end{itemize}


% ==============================================
\section{Research Projects}

\customcvproject{Automatic air quality monitoring at Curtis Bay}{}{}
Baltimore, MD | Oct. 2023 - Present
\begin{itemize}
\item Spearhead a team consisting of 3 students and 2 faculty members in the creation of a real-time air quality monitoring system, employing machine learning and computer vision technologies
\item Engineer picture labeling mechanisms utilizing optical character recognition (OCR) and image processing pipelines to streamline air quality monitoring procedures.
\item Design and implement a computer vision model capable of detecting and categorizing coal mine activity, complemented by a machine learning model to correlate air quality fluctuations with coal mining operations, facilitating support for community air quality regulations.
\end{itemize}

\customcvproject{SigROCKET: a scalable time series classification method}{}{}
Baltimore, MD | Mar. 2023 - Present
\begin{itemize}
\item Developed a machine learning model capable of classifying time series data characterized by gaps in time, large fluctuations in magnitude, and similar ranges of fluctuations. Real-world applications include distinguishing between different types of diseases based on ICU measurements.
\item Integrated the non-linear feature extraction method, Signature, with Multi-Rocket to construct a scalable time series classification algorithm.
\item Devised a scalable algorithm suitable for analyzing long multivariate time series data, achieving state-of-the-art classification performance with up to a 35\% increase in AUC, while reducing computational costs. This was accomplished by combining signature transformation with Multi-Rocket.
\item One publication currently under preparation.
\end{itemize}

\customcvproject{Uncertainty estimation of transit time distribution in a bi-modal hydrologic response watershed}{}{}
Baltimore, MD | Aug. 2021 - Present
\begin{itemize}
\item Disaggregated weekly bulk samples into 6-hourly intervals using Gaussian Process regression. Additionally, propagated a 28x downscaled input and its 95\% uncertainty bound using Gaussian Process regression, passing hypothesis tests at a 0.99 confidence level. Finally, propagated the downscaled input through a fluid transport model.
\item Developed a model to characterize the transit time distribution of a watershed, enabling the understanding of how this watershed transports, stores, and releases substances.
\end{itemize}

\customcvproject{Bayesian uncertainty quantification on MESAS model}{}{}
Baltimore, MD | Sep. 2018 - Present
\begin{itemize}
\item Enhanced stream water solute concentration estimation by implementing a data-driven approach using local linear piecewise StorAge Selection (SAS) functions, eliminating the need for a-priori assumptions.
\item Strengthened a numerical fluid transport model with a multiscale adaptive kernel algorithm, facilitating non-parametric estimation of hidden states at flexible local scales through various non-linear statistical inference methods. Developed a bash pipeline for conducting experiments on a high-performance computing grid powered by SLURM. Submitted software publication demonstrating a 10x reduction in cumulative numerical error for a 4-year test dataset.
\item Devised a particle Markov Chain Monte Carlo (MCMC) framework for propagating input and output uncertainty, enabling informed risk control by providing accurate inference about the structure of complex dynamic systems.
\item Conducted simultaneous uncertainty quantification on multiple sources, including input/output time series and black-box model structure.
\item Authored one software publication, with one publication currently under preparation.
\end{itemize}

\customcvproject{Construct coarse representation of subsurface soil-rock interface}{}{}
Baltimore, MD | May 2020 - Feb.2024
\begin{itemize}
\item Derive effective coarse-scale representation of permeability at subsurface permeability contrast to facilitate demand for detailed data (requires intensive drilling) in previous fill-and-spill modeling.
\item Test proof-derived anisotropic permeability tensor from realizations generated from virtual truth based on the Richards equation using the ParFlow model.
\item Developed bash pipeline on high performance computing grid MARCC to process parallel computing tasks for more than 30,000 computational hours.
\end{itemize}

\customcvproject{Theoretical optimal benchmarking in time series classiﬁcation}{}{}
Baltimore, MD | May 2022  - Feb. 2023
\begin{itemize}
\item Establish theoretical optimal benchmark to evaluate SOTA time series classification (TSC) methods (random forest, ROCKET, neural network) for stochastic process
\item Provide synthetic dataset (Ornstein-Uhlenbeck processes, different potentials, Brownian motion + constant drift, Opinion dynamics) for systematical testing on TSC methods
\item Authored in one preprint publication.
\end{itemize}

\customcvproject{Novel end-member identification model, CHEMMA}{}{}
Baltimore, MD | May 2018 - May 2021
\begin{itemize}
\item Advanced traditional end-member identification method by building unsupervised data-driven model in Python, Convex-Hull End-Member Mixing Analysis (CHEMMA) by reducing data annotation 100\%
\item Successfully identified 3 field-measured end-members combining ConvexHull-NMF and constrained Kmeans; Reduce streamwater chemistry variation 6x on each end-members; Achieve same result using 50\% less data
\item Published one first author publication on Hydrology and Earth System Sciences; Model is recognized as SOTA on invited review paper
\item Code publicly available on \href{https://github.com/Estherrrrrxu/CHEMMA}{\underline{GitHub}}
\end{itemize}

\customcvproject{Data analysis on hydrological connectivity of Bonneville salt flats}{}{}
Baltimore, MD | Oct. 2018 - Dec. 2018
\begin{itemize}
  \item Identified surface deformation through Principal Component Analysis (PCA) and Independent Component Analysis (ICA) on remotely sensed dataset (InSAR) of Bonneville salt flat
\end{itemize}

\customcvproject{Statewide groundwater recharge estimation (M.S. Thesis)}{}{}
Socorro, NM | Jun. 2016 - Aug. 2018
\begin{itemize}
    \item Developed Python-programmed groundwater recharge model to estimate rate and distribution of groundwater recharge for entire state of New Mexico with team of 9; Improved algorithm in giving estimation at karst landscape with error less than 10\%; Cooperated with New Mexico Tech evapotranspiration (ET) research group to improve estimation of ET and total available water in root zone
    \item Estimated precipitation-runoff relationship by building linear regression model with threshold, and reduced overland flow by 7 times.
    \item Processed 2T GIS files using Gdal, ArcGIS, and QGIS; Acquired soil physical property data from USDA NRCS soil database STATSGO and SSURGO
    \item Authored one publication summarizing project as first author (under preparation) and one masters thesis
  \end{itemize}
  
\section{Awards and Honors}
\award{M. Gordon Wolman Fellowship}{Aug. 2023 - May 2024}
\award{Doctoral Leadership Award, JHU EHE}{May 2023}
\award{Natalie M. Lorenz Anderson Fellowship}{Aug. 2021 - May 2022}
\award{CUAHSI student travel grant}{Jan. 2019 - Oct. 2019}
\award{Edwin D. and Rachel Lowthian Endowed Fellowship}{Aug. 2018 - Aug. 2019}
\award{UC Berkeley workshop scholarship}{May 2019}
\award{Environmental Health and Engineering Student Organization Travel Grant}{Apr. 2019}
\award{Lee and Albert H. Halff Doctoral Student Award}{Aug. 2018}
\award{New Mexico Tech Graduate Student Study Travel Grant}{Sep. 2017}
\award{New Mexico Tech Honor Roll}{Aug. 2014 - May 2016}
\award{Durtche Geophysics Award (Best geophysics student of the year)}{May 2016}
\award{NMGS student Fall Field Conference Scholarship}{Oct. 2015}
\award{Carlsbad Mineral and Gem Society Award (Best geology student of the year)}{May 2015}
\award{Best debater in Yangtze University Debate Finals (1/20)}{Mar. 2014}
\award{Yangtze University Scholarship}{Sep. 2012 - Jun. 2014}

\bibliographystyle{unsrtnat}
% Cite in reverse chronological order (newest first)
\nocite{harman2022mesas}
\nocite{zhang2023benchmarking}
\nocite{fu2023evaluating}
\nocite{xufei}
\nocite{fu2022critical}
\nocite{masterthesis}
\bibliography{publications} 

                              
\section{Teaching and Mentoring Experiences}
\subsection{Teaching Assistant}
\award{Data Analytics in Environmental Health and Engineering}{Jan. 2024 - May 2024}
\award{Data Analytics in Environmental Health and Engineering}{Jan. 2023 - May 2023}
\award{Data Analytics in Environmental Health and Engineering}{Jan. 2022 - May 2022}
\award{Data Analytics in Environmental Health and Engineering}{Jan. 2021 - May 2021}
\award{Landscape Hydrology and Watershed Analysis}{Jan. 2020 - May 2020}
\award{Landscape Hydrology and Watershed Analysis}{Aug. 2018 - Dec. 2018}
\award{Introduction to Fluid Mechanics}{Aug. 2018 - Dec. 2018}
\subsection{Mentor}

\award{Ph.D. Candidate from Cornell University, Nish Singh}{Nov. 2023 - Present}
\award{M.S.E. student from Johns Hopkins University, Sakshi Labhane}{Jun. 2021 - Dec. 2021}
\award{Undergraduate student, Kayla Ostrow}{Dec. 2019 - Mar. 2020}
\award{High school student, Julia Alumbro}{Aug. 2019 -  Dec. 2019}

\section{Leadership and Services}
\subsection{Leadership}
\customcventry{}{Session H23D, AGU Fall Meeting 2024}{Primary Convenor}{Mar. 2023 - Dec. 2023}{}{}

\customcventry{}{Cross-Institutional Student Advisory Committee, JHU, Baltimore, MD}{Student representative}{Jan. 2023 - Aug. 2024}{}{}

\customcventry{}{Graduate Representative Organization (GRO), JHU, Baltimore, MD}{Treasurer}{May. 2022 - May 2024}{}{}

\customcventry{}{EHE Student Service Organization (EHESO), JHU, Baltimore, MD}{President}{May 2022 - May 2023}{}{}

\customcventry{}{EHE Welcome Ceremony, JHU, Baltimore, MD}{Student speaker}{Aug. 2022}{}{}

\customcventry{}{Astrobiology Graduate Conference (AbGradCon) 2022, Washington, D.C.}{Local conference organizer}{Jun. 2021 - May 2022}{}{}

\customcventry{}{GRO, JHU, Baltimore, MD}{Secretary}{Aug. 2021 - May 2022}{}{}

\customcventry{}{EHE Graduation Ceremony, JHU, Baltimore, MD}{Student speaker}{May. 2021}{}{}

\customcventry{}{EHESO, JHU, Baltimore, MD}{President-elect}{May 2021 - May 2022}{}{}

\customcventry{}{Landscape Hydrology Lab, JHU, Baltimore, MD}{Lab Assistant}{Aug. 2018 - May 2021}{}{}

\customcventry{}{EHESO, JHU, Baltimore, MD}{Ph.D. Representative}{Aug. 2020 - May 2021}{}{}

\customcventry{}{NM Statewide Water Assessment Workshop, Socorro, NM}{Co-host}{Oct. 2016}{}{}

\customcventry{}{Residential Life, New Mexico Tech, Socorro, NM}{Resident Assistant}{Aug. 2015 - Aug. 2016}{}{}

\customcventry{}{School Magazine, Yangtze University, Hubei, Wuhan, China}{Chief Editor}{Sep. 2013 - Aug. 2014}{}{}

\subsection{Volunteer}
\customcventry{}{Grace Hopper Celebration 2023, Orlando, FL}{Hopper}{Sep. 2023}{}{}
\customcventry{}{EHESO, JHU, Baltimore, MD}{Coffee Hour Host}{Dec. 2020}{}{}
\customcventry{}{Magdalena Ridge Observatory, Magdalena, NM}{Science Tour Guide}{Feb. 2015 - May 2015}{}{}

\section{Presentations}
\subsection{Oral presentations}
\customcvproject{Guess lecturer for Data Analytics, JHU, Baltimore, MD}{| Feb. 2023}{}
\begin{itemize}
  \item Covered lectures for linear and non-linear regression, logistic regression, boostrap, cross validation, model selection and regularization
\end{itemize}

\customcvproject{2022 American Geophysical Union Fall Meeting, Chicago, IL}{| Dec. 2022}{}
\begin{itemize}
  \item Dynamic uncertainty quantification of catchment transit time and StorAge Selection distributions using an adaptive non-parametric Bayesian framework
\end{itemize}

\customcvproject{2022 Frontiers in Hydrology, San Juan, PR}{| Jun. 2022}{}
\begin{itemize}
  \item CHEMMA: a method for estimating end-member source composition from mixture data alone
\end{itemize}

\customcvproject{2021 American Geophysical Union Fall Meeting, New Orleans, LA}{| Dec. 2021}{}
\begin{itemize}
  \item Estimating the transit time distribution in a forested watershed with a bimodal hydrologic response using Multi-scale Estimation of StorAge Selection function (MESAS)
\end{itemize}

\customcvproject{JHU Environmental Health and Engineering department seminar, Baltimore, MD}{| Feb. 2021}{}
\begin{itemize}
  \item Where does the water in your cup come from?
\end{itemize}

\customcvproject{JHU Environmental Health and Engineering department seminar, Baltimore, MD}{| Nov. 2019}{}
\begin{itemize}
  \item  CHEMMA 101: Introduction to Convex Hull End Member Mixing Analysis
\end{itemize}

\customcvproject{JHU Environmental Health and Engineering department seminar, Baltimore, MD}{| Sep. 2018}{}
\begin{itemize}
  \item Estimation of focused recharge for New Mexico using a soil-water-balance model: PyRANA
\end{itemize}

\customcvproject{2017 American Geophysical Union Fall Meeting, New Orleans, LA}{| Dec. 2017}{}
\begin{itemize}
  \item Statewide groundwater recharge modeling in New Mexico
\end{itemize}

\customcvproject{NM Statewide Water Assessment Workshop, Socorro, NM}{| Oct. 2016}{}
\begin{itemize}
  \item Water estimation matters
\end{itemize}

\subsection{Poster presentations}
\customcvproject{2023 American Geophysical Union Fall Meeting}{| Dec. 2023}{}
\begin{itemize}
  \item SigROCKET: a scalable time series classification algorithm using path signature and random convolution kernel
  \item An adaptive Bayesian approach for stochastic dynamic system uncertainty quantification with applications to noisy, incomplete, or excessively-smoothed data
\end{itemize}

\customcvproject{2020 American Geophysical Union Fall Meeting}{| Dec. 2020}{}
\begin{itemize}
  \item Can fill-and-spill subsurface flow be represented by a moisture-dependent anisotropic permeability tensor in Richards' equation-based models with coarse spatial resolution?
\end{itemize}

\customcvproject{2019 American Geophysical Union Fall Meeting}{| Dec. 2019}{}
\begin{itemize}
  \item Learning from the data: manifold learning in interpreting tracers of the landscape hydrologic system
\end{itemize}

\customcvproject{2018 American Geophysical Union Fall Meeting}{| Dec. 2018}{}
\begin{itemize}
  \item High-resolution statewide groundwater recharge estimation by soil water balance in New Mexico
\end{itemize}

\customcvproject{$\mathbf{62^{nd}}$ New Mexico Water Conference}{Aug. 2017}{}
\begin{itemize}
  \item Efforts on calibration and validation of modeling groundwater recharge in New Mexico
\end{itemize}

\customcvproject{$\mathbf{61^{st}}$ New Mexico Water Conference}{Oct. 2016}{}
\begin{itemize}
  \item Modeling focused recharge through ephemeral streams in New Mexico
\end{itemize}
\section{Participated Workshops}
\customcventry{}{Princeton University, Princeton, NJ}{Princeton GPU Hackathon 2022}{Jun. 2022}{}{}

\customcventry{}{Pennsylvania State University, University Park, PA}{HydroML}{May 2022}{}{}

\customcventry{}{University of Arizona, Tucson, AZ}{Advanced short course: integrated simulation of watershed systems using ParFlow}{Oct. 2019}{}{}

\customcventry{}{Northwestern University, Evanston, IL}{4th annual Communicating Science Conference in Chicago}{Aug. 2019}{}{}

\customcventry{}{Colorado School of Mines, Golden, CO}{Short course: integrated simulation of watershed systems using ParFlow}{May 2019}{}{}

\customcventry{}{University of California, Berkeley, Berkeley, CA}{Workshop on critical timescales of hydrologic transport}{May 2019}{}{}

\customcventry{}{University of Waterloo, Waterloo, Ontario, CA}{Short course: environmental models and Bayesian methods}{Mar. 2019}{}{}

\customcventry{}{Biosphere2, Oracle, AZ}{Master class: advanced techniques in watershed science}{Jan. 2019}{}{}
% Publications from a BibTeX file without multibib
%  for numerical labels: \renewcommand{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}% CONSIDER MERGING WITH PREAMBLE PART
%  to redefine the heading string ("Publications"): \renewcommand{\refname}{Articles}


% Publications from a BibTeX file using the multibib package
%
%\nocitebook{book1,book2}
%\bibliographystylebook{plain}
%\bibliographybook{publications}                   % 'publications' is the name of a BibTeX file
%\nocitemisc{misc1,misc2,misc3}
%\bibliographystylemisc{plain}
%\bibliographymisc{publications}                   % 'publications' is the name of a BibTeX file

%-----       letter       ---------------------------------------------------------

\end{document}


%% end of file `template.tex'.
